---
title: "data products week 3"
author: "K S SRIKANTH"
date: "05/11/2020"
output: html_document
---

## Variation of Miles per Gallon with respect to some characteristics of the car.

The rubric contains the following two questions:

1.Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

2.Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?
```{r}
library(plotly)
data(mtcars)
head(mtcars)
```
```{r}
plot_ly(mtcars) %>%
    add_trace(x = ~mpg, y = ~cyl, type="scatter", mode = "markers",name = "circular", legendgroup = "circular", 
              marker = list(color = "green")) %>%
    add_trace(x = ~mpg, y = ~gear, type="scatter", mode = "markers",
              name = "data_point2", legendgroup = "data_point2", 
              marker = list(color = "orange")) %>%
    add_trace(x = ~mpg, y = ~carb, type="scatter", mode = "markers",
              name = "datapoint3", legendgroup = "datapoint3", 
              marker = list(color = "yellow")) 
```

I have used scatter plot to represent the data.

i used different colours to distunguish various datas and points.

as per the results the answer for first question is yes as it has data of last two months.

I have created a interactive plot  using scatter plot. it used used so, to disttunguish each data from one another.and to produce results in more simpler manner.

it has taken around four hours of my time and i think the resuls are pretty satisfactory.

The project gave a simple understading of hoe the data can be used and gave experience and also a lot of self confidence






